\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-12 doc/flexiblesusy-paper.tex
fixed order of refs I just added.
added Gregor Hellwig and Gambit to acknowledgements.

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models. The authors would also
like to thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Philip Diessner
for testing and identifying several bugs in \fs and in SARAH,
in work on the MRSSM; Ulrik Günther for compilation tests on Mac OS X
and Dylan Harries for spotting a bug in the configuration script.
%
J.P. acknowledges support from the MEC and FEDER (EC) Grants
FPA2011--23596 and the Generalitat Valenciana under grant PROMETEOII/2013/017.
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.

>>>>

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models and the GAMBIT
collaboration for helpful suggestions, particularly regarding
lowering our compiler prerequisites. The authors would also like to
thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Gregor Hellwig
for writing the first version of the E6SSM model file; Philip Diessner
for further adaptions to the E6SSM model file and for supplying it to
us and for for testing and identifying several bugs in \fs and in
SARAH, in work on the MRSSM; Ulrik Günther for compilation tests on
Mac OS X and Dylan Harries for spotting a bug in the configuration
script.
%
J.P. acknowledges support from the MEC and FEDER (EC) Grants
FPA2011--23596 and the Generalitat Valenciana under grant PROMETEOII/2013/017.
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.
